A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-01-20 01_TrialsForInclusionInAnalysis.Rmd
removed unnecessary group code in summarise() function

We need to focus the meta-analysis on fungicides with the same mode of action.
Let's look at all the fungicides and retain the best represented fungicide group in the data.
```{r Fungicides}
PM_MB_dat %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise(groups = 'drop') %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
   scale_colour_usq() +
   coord_flip()
```

>>>>

We need to focus the meta-analysis on fungicides with the same mode of action.
Let's look at all the fungicides and retain the best represented fungicide group in the data.
```{r Fungicides}
PM_MB_dat %>%
   group_by(fungicide_ai,trial_ref) %>%
   summarise() %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
   scale_colour_usq() +
   coord_flip()
```
